### 2018-01-04 submission/manuscript.Rmd
conclusion re-write

By aggregating together a large collection of studies from both feces and tissue, we are able to provide evidence in support of the importance of the bacterial community in both adenoma and carcinoma. Overall, our results support a framework by which early localized community changes give rise to polyp formation. With the host as a potential catalyst, new niches arise by which non-resident CRC-associated microbes can then gain a foothold and create an environment that allows more of these microbes to colonize. This exacerbates the existing community changes and creates a vicious cycle conducive of carcinoma formation. Our observations also highlight the importance of power and sample number considerations when undertaking investigations into the microbiota and adenoma due to the subtle changes in the community. Although there are power limitations associated with adenoma, this report highlights the strong associations the microbiota has on CRC.

>>>>

By aggregating together a large collection of studies from both feces and tissue, we are able to provide evidence in support of the importance of the bacterial community in CRC. Further, the data presented here suggests that non-resident mouth-associated microbes can gain a foothold within the colon and the more of these microbes that are present the greater the RR of carcinoma. Conversely, no clear signal with these mouth-associated micobes could be detected for adenoma. Our observations also highlight the importance of power and sample number considerations when undertaking investigations into the microbiota and adenoma due to the subtle changes in the community. Overall, the microbiota associations with carcinoma are much stronger than the associations with adenoma.
